\documentclass[10pt,letterpaper]{article}

\input{common.tex}
\titlespacing*{\section}{0pt}{9pt}{5pt}

\begin{document}
\sloppy
\setupcvfooter{March 2026}

\makeprofileheader
  {Rajeev Jain}
  {Website: \href{https://rajeeja.github.io}{rajeeja.github.io} \hspace{10pt} GitHub: \href{https://github.com/rajeeja}{rajeeja} \hspace{10pt} LinkedIn: \href{https://linkedin.com/in/rajeeja}{rajeeja} \hspace{10pt} Scholar: \href{https://scholar.google.com/citations?user=bC77n9MAAAAJ\&hl=en}{Google Scholar}}
  {E-mail: \href{mailto:rajeeja@gmail.com}{rajeeja@gmail.com}}

{\large Research Software Engineer | ML Infrastructure | Scientific Computing}\par
\vspace{5pt}

\section{Professional Profile}
Research software engineer with 16+ years of experience building software for climate science, AI for cancer research, computational physics, and exascale systems. My work spans Python platforms, C++ and Fortran HPC codebases, large-scale ML experimentation, release engineering, numerical methods, and performance optimization. The resulting software has been used across national labs, universities, and multi-institution collaborations.

\section{Education}
\textbf{University of Chicago} \hfill 2020 \\
M.S. in Computer Science

\vspace{4pt}
\textbf{Arizona State University} \hfill 2009 \\
M.S. in Structural Engineering \\
Advisors: Dr. S.D. Rajan (ASU), Dr. Ashok Belegundu (PSU) \\
Graduate Fellowship Recipient (2007--2009)

\vspace{4pt}
\textbf{Indian Institute of Technology (ISM) Dhanbad} \hfill 2006 \\
B.Tech. in Mechanical Engineering \\
IIT JEE 2002 Rank: 3487

\section{Professional Experience}
\entryheader
  {Argonne National Laboratory}
  {2009 -- Present}
  {Principal Specialist, Research Software Engineering}
  {Mathematics and Computer Science Division, Chicago, IL}
\begin{itemize}
  \item Research software engineer across climate analytics, scientific AI, simulation infrastructure, and DOE research software programs.
  \item Work includes architecture, implementation, testing, release engineering, performance optimization, and cross-institution coordination.
  \item Major efforts include UXarray, FLASH-X, CANDLE / IMPROVE, Pangu-Weather on Aurora, MeshKit, and urban microclimate software workflows.
\end{itemize}

\entryheader
  {University of Chicago}
  {2023 -- Present}
  {Staff At-Large}
  {Chicago, IL}
\begin{itemize}
  \item Joint appointment supporting cancer pharmacogenomics and Earth science collaborations.
  \item Mentor students and research staff on software design, experimentation, and reproducibility.
\end{itemize}

\entryheader
  {Arizona State University}
  {2007 -- 2009}
  {Research and Teaching Assistant}
  {Structural and Computational Mechanics Lab, Tempe, AZ}
\begin{itemize}
  \item Conducted FEM-based research in blast mitigation and supported structural analysis coursework.
\end{itemize}

\entryheader
  {Earlier Industry Experience}
  {2005 -- 2007}
  {Project Engineer, Wipro Technologies; Engineering Intern, Tata Motors}
  {India}
\vspace{0.3em}

\section{Research Software Leadership and Projects}
\entryheader
  {UXarray}
  {2022 -- Present}
  {Lead Developer}
  {Open-source climate analysis platform}
\begin{itemize}
  \item Lead developer for a Python library enabling analysis of native unstructured climate and weather grids.
  \item Designed the core API, conservative zonal averaging via Gauss-Legendre quadrature, geometry operators, grid I/O for ESMF / MPAS / SCRIP / HEALPix, automated tests, CI/CD, and release workflows.
  \item Project used by NCAR, DOE labs, and universities. Tutorials and presentations delivered at SC24, AMS, SciPy, EGU, AGU, and related venues.
\end{itemize}

\entryheader
  {Pangu-Weather on Aurora}
  {2024 -- Present}
  {Software Engineer}
  {AI weather modeling on exascale Intel GPUs}
\begin{itemize}
  \item Reimplemented the Pangu-Weather framework in PyTorch using the Spectral Fourier Neural Operator for Aurora.
  \item Adapted the workflow to Intel GPUs and ran it at large scale on Aurora.
\end{itemize}

\entryheader
  {CANDLE / IMPROVE}
  {2020 -- 2025}
  {Core Contributor}
  {Cancer AI infrastructure and benchmarking}
\begin{itemize}
  \item Built hyperparameter optimization and benchmarking infrastructure for cancer drug response prediction.
  \item Ran 10,000+ model training experiments across Summit, Theta, and Cori, with automated cross-study validation and reproducible workflows.
  \item Supported a 15+ researcher multi-lab collaboration spanning Argonne, LLNL, and ORNL. Work contributed to an R\&D 100 Award in 2023.
\end{itemize}

\entryheader
  {FLASH-X}
  {2019 -- 2024}
  {I/O and Compression Lead}
  {Multiphysics simulation software}
\begin{itemize}
  \item Implemented asynchronous HDF5 I/O with Argobots and integrated SZ3 / ZFP compression for checkpoint and restart workflows.
  \item Reduced checkpoint overhead by 40-70\% on Summit and achieved storage savings above 50\%.
  \item Enabled cross-checkpoint restart between AMReX and Paramesh solvers. Work contributed to an R\&D 100 Award in 2022.
\end{itemize}

\entryheader
  {MeshKit and Urban ECP}
  {2009 -- 2019}
  {Principal Investigator / Software Lead}
  {DOE reactor and urban systems programs}
\begin{itemize}
  \item Principal investigator for MeshKit within DOE NEAMS, leading reactor mesh generation tools and parallel workflows for nuclear simulation.
  \item Coordinated software work across multiple national labs for urban microclimate and CFD workflows, including proposal development and shared workflows.
  \item Developed parallel reactor core mesh generation workflows and urban modeling integrations linking mesoscale weather and CFD simulation.
\end{itemize}

\section{Funding and Research Programs}
\begin{itemize}
  \item \textbf{DOE SEATS} (active): Software Ecosystem for Advancing Climate Tools and Services.
  \item \textbf{NSF Raijin} (active): collaborative research in climate model analysis.
  \item \textbf{DOE ECP CANDLE} (2017 -- 2023): core contributor on cancer AI infrastructure.
  \item \textbf{DOE NEAMS} (2009 -- 2016): principal investigator for MeshKit and reactor mesh generation workflows.
  \item \textbf{Urban ECP}: software lead and coordinator for urban microclimate and CFD workflows across multiple labs.
\end{itemize}

\section{Awards \& Recognition}
\begin{itemize}
  \item R\&D 100 Award, CANDLE (2023).
  \item R\&D 100 Award, FLASH-X (2022).
  \item ATPESC Scholar, Argonne Training Program on Extreme-Scale Computing (2015).
  \item Best Paper Award, International Meshing Roundtable (2010).
  \item Graduate Fellowship, Arizona State University (2007 -- 2009).
  \item U.S. permanent resident; no sponsorship required.
\end{itemize}

\section{Peer-Reviewed Journal Articles}
\pubentry{2025}{Partin, A., Vasanthakumari, P., Narykov, O., Wilke, A., Koussa, N., Jones, S., Zhu, Y., \textbf{Jain, R.}, Overbeek, J. C., Fernando, G. D., Sanchez-Villalobos, C., Garcia-Cardona, C., Mohd-Yusof, J., Chia, N., Wozniak, J. M., Ghosh, S., Pal, R., Brettin, T. S., Weil, M. R., and Stevens, R. L. ``\href{https://academic.oup.com/bib/article/27/1/bbaf667/7002013}{Benchmarking community drug response prediction models: datasets, models, tools, and metrics for cross-dataset generalization analysis}.'' \textit{Briefings in Bioinformatics}.}
\pubentry{2022}{Dubey, A., Weide, K., O'Neal, J., Dhruv, A., Couch, S., Harris, J. A., Klosterman, T., \textbf{Jain, R.}, Rudi, J., Messer, B., Pajkos, M., Carlson, J., Chu, R., Wahib, M., Chawdhary, S., Ricker, P. M., Lee, D., Antypas, K., Riley, K. M., Daley, C., Ganapathy, M., Timmes, F. X., Townsley, D. M., Vanella, M., Bachan, J., Rich, P. M., Kumar, S., Endeve, E., Hix, W. R., Mezzacappa, A., and Papatheodore, T. ``Flash-X: A multiphysics simulation software instrument.'' \textit{SoftwareX}.}
\pubentry{2022}{Harris, J. A., Chu, R., Couch, S. M., Dubey, A., Endeve, E., Georgiadou, A., \textbf{Jain, R.}, Kasen, D., Laiu, M. P., Messer, O. E. B., O'Neal, J., Sandoval, M. A., and Weide, K. ``Exascale models of stellar explosions: quintessential multi-physics simulation.'' \textit{International Journal of High Performance Computing Applications}.}
\pubentry{2020}{\textbf{Jain, R.}, Luo, X., Sever, G., Hong, T., and Catlett, C. ``Representation and evolution of urban weather boundary conditions in downtown Chicago.'' \textit{Journal of Building Performance Simulation}.}
\pubentry{2018}{Wozniak, J. M., \textbf{Jain, R.}, Balaprakash, P., Ozik, J., Collier, N. T., Bauer, J., Xia, F., Brettin, T., Stevens, R., Mohd-Yusof, J., Garcia-Cardona, C., Van Essen, B., and Baughman, M. ``CANDLE/Supervisor: A workflow framework for machine learning applied to cancer research.'' \textit{BMC Bioinformatics}.}
\pubentry{2014}{Mahadevan, V. S., Merzari, E., Tautges, T., \textbf{Jain, R.}, Obabko, A., Smith, M., and Fischer, P. ``High-resolution coupled physics solvers for analysing fine-scale nuclear reactor design problems.'' \textit{Philosophical Transactions of the Royal Society A}.}
\pubentry{2012}{Tautges, T. J. and \textbf{Jain, R.} ``\href{https://doi.org/10.1007/s00366-011-0236-8}{Creating geometry and mesh models for nuclear reactor core geometries using a lattice hierarchy-based approach}.'' \textit{Engineering with Computers}.}
\pubentry{2008}{Argod, V., Belegundu, A. D., Aziz, A., Agrawala, V., \textbf{Jain, R.}, and Rajan, S. D. ``MPI-enabled shape optimization of panels subjected to air blast loading.'' \textit{International Journal for Simulation and Multidisciplinary Design Optimization}.}

\section{Peer-Reviewed Conference and Workshop Proceedings}
\pubentry{2025}{Gwinn, J., Wozniak, J. M., \textbf{Jain, R.}, Zhu, Y., Partin, A., Brettin, T., and Stevens, R. ``A Workflow for Error Analysis for Drug Response Prediction via Statistical Standardization and Distribution Analysis.'' \textit{Workshop on Workflows in Support of Large-Scale Science (WORKS)}.}
\pubentry{2024}{\textbf{Jain, R.}, Tang, H., Dhruv, A., and Byna, S. ``\href{https://doi.org/10.1109/SCW63240.2024.00043}{Enabling Data Reduction for Flash-X Simulations}.'' \textit{SC24 Workshops: DRBSD-10}.}
\pubentry{2024}{\textbf{Jain, R.}, Wozniak, J. M., Partin, A., Wilke, A., Zhu, Y., Vasanthakumari, P., Narykov, O., Overbeek, J., Weaver, R., Wang, C., Liu, Y., Weil, M. R., Brettin, T., and Stevens, R. ``\href{https://web.cels.anl.gov/~woz/papers/IMPROVE_HPO_2024.pdf}{Cross-HPO: Optimizing Neural Networks for Cancer Drug Response Using Hyperparameter Tuning on Multiple Pharmacogenomic Datasets}.'' \textit{Computational Approaches for Cancer Workshop at SC24}.}
\pubentry{2023}{Wozniak, J. M., \textbf{Jain, R.}, Wilke, A., Weaver, R., Partin, A., Brettin, T., and Stevens, R. ``An Automation Framework for Comparison of Cancer Response Models Across Configurations.'' \textit{IEEE e-Science}.}
\pubentry{2023}{Dhruv, A., \textbf{Jain, R.}, O'Neal, J., Weide, K., and Dubey, A. ``Framework and Methodology for Verification of a Complex Scientific Simulation Software, Flash-X.'' \textit{Congress in Computer Science, Computer Engineering, and Applied Computing}.}
\pubentry{2022}{\textbf{Jain, R.}, Tang, H., Dhruv, A., Harris, J. A., and Byna, S. ``Accelerating Flash-X Simulations with Asynchronous I/O.'' \textit{PDSW}.}
\pubentry{2021}{\textbf{Jain, R.}, Shah, A., Mohd-Yusof, J., Wozniak, J. M., Brettin, T., Xia, F., and Stevens, R. ``Probing Decision Boundaries in Cancer Data Using Noise Injection and Counterfactual Analysis.'' \textit{CAFCW at SC21}.}
\pubentry{2021}{\textbf{Jain, R.}, Weide, K., Chawdhary, S., and Klostermann, T. ``Checkpoint / Restart for Lagrangian Particle Mesh with AMR in Community Code FLASH-X.'' \textit{SuperCheck}.}
\pubentry{2015}{\textbf{Jain, R.} and Tautges, T. J. ``NEAMS MeshKit: Nuclear Reactor Mesh Generation Solutions.'' \textit{International Congress on Advances in Nuclear Power Plants}.}
\pubentry{2015}{\textbf{Jain, R.}, Mahadevan, V., and O'Bara, R. ``Simplifying Workflow for Reactor Assembly and Full-Core Modeling.'' \textit{Mathematics and Computation (MC2015)}.}
\pubentry{2014}{\textbf{Jain, R.} and Tautges, T. J. ``Generating Unstructured Nuclear Reactor Core Meshes in Parallel.'' \textit{Procedia Engineering}.}
\pubentry{2013}{\textbf{Jain, R.} and Tautges, T. J. ``PostBL: Post-Mesh Boundary Layer Mesh Generation Tool.'' \textit{International Meshing Roundtable}.}
\pubentry{2012}{\textbf{Jain, R.} and Tautges, T. J. ``RGG: Reactor Geometry (and Mesh) Generator.'' \textit{International Congress on Advances in Nuclear Power Plants}.}
\pubentry{2012}{Mohanty, S., \textbf{Jain, R.}, Majumdar, S., Tautges, T. J., and Srinivasan, M. ``Coupled Field Structural Analysis of HTGR Fuel Brick Using Abaqus.'' \textit{International Congress on Advances in Nuclear Power Plants}.}
\pubentry{2010}{Tautges, T. J. and \textbf{Jain, R.} ``Creating Geometry and Mesh Models for Nuclear Reactor Core Geometries Using a Lattice Hierarchy-Based Approach.'' \textit{19th International Meshing Roundtable}. Best Paper Award.}

\section{Conference Abstracts, Tutorials, and Presentations}
\pubentry{2025}{Eroglu, O., Chen, H., Chmielowiec, P., Hannay, C., Jacob, R. L., \textbf{Jain, R.}, Medeiros, B., Ullrich, P., and Zarzycki, C. M. ``UXarray: Extending Xarray to Support the Analysis of Native, Kilometer-Scale Unstructured Grids in Python.'' \textit{105th AMS Annual Meeting}.}
\pubentry{2025}{Clyne, J., Chen, H., Chmielowiec, P., Eroglu, O., Hannay, C., Jacob, R., \textbf{Jain, R.}, Medeiros, B., Ullrich, P., and Zarzycki, C. ``UXarray: Extending Xarray for Enhanced Support of Unstructured Grids.'' \textit{EGU General Assembly}.}
\pubentry{2024}{\textbf{Jain, R.} ``Tutorial: UXarray for Analysis of Unstructured Climate Data.'' \textit{SC24}.}
\pubentry{2024}{Chmielowiec, P., Chen, H., DeCiampa, C., Eroglu, O., Hannay, C., Jacob, R. L., \textbf{Jain, R.}, Loft, R., Medeiros, B., Sun, L., Ullrich, P., and Zarzycki, C. M. ``UXarray: Extending Xarray with Support for Unstructured Grids.'' \textit{104th AMS Annual Meeting}.}
\pubentry{2024}{Eroglu, O., Chen, H., Chmielowiec, P., Clyne, J., DeCiampa, C., Hannay, C., Jacob, R., \textbf{Jain, R.}, Loft, R., Medeiros, B., Sun, L., Ullrich, P., and Zarzycki, C. ``UXarray: Extensions to Xarray to Support Unstructured Grids.'' \textit{EGU General Assembly}.}
\pubentry{2024}{Clyne, J., Chen, H., Chmielowiec, P., Hannay, C., Jacob, R. L., \textbf{Jain, R.}, Medeiros, B., Ullrich, P. A., and Zarzycki, C. M. ``UXarray: An Extension to Xarray Supporting Analysis and Visualization of Kilometer-Scale Model Outputs.'' \textit{AGU Fall Meeting}.}
\pubentry{2024}{\textbf{Jain, R.} ``UXarray Tutorial.'' \textit{ESDS Annual Event}. \href{https://www.youtube.com/watch?v=sOCMSLZrwQs}{Video}.}
\pubentry{2023}{\textbf{Jain, R.} ``\href{https://www.youtube.com/watch?v=qwqJeOO8m6A}{UXarray for Unstructured Climate Data}.'' \textit{SciPy 2023}.}
\pubentry{2023}{\textbf{Jain, R.} ``\href{https://www.youtube.com/watch?v=MuifQ7lHRR8}{Data Reduction for FLASH-X Simulations}.'' \textit{HDF User Group 2023}.}
\pubentry{2023}{Clyne, J., Chen, H., Chmielowiec, P., DeCiampa, C., Eroglu, O., Hannay, C., Jacob, R. L., \textbf{Jain, R.}, Medeiros, B., Sun, L., Ullrich, P. A., and Zarzycki, C. M. ``UXarray: A Community-Developed Tool for the Analysis and Visualization of Model Output on Unstructured Grids in Python.'' \textit{AGU Fall Meeting}.}
\pubentry{2023}{Jacob, R. L., Ullrich, P. A., Zhang, C., \textbf{Jain, R.}, Chen, H., Po-Chedley, S., and Vo, T. ``Creating New Standards to Simplify Earth System Model Analysis.'' \textit{AGU Fall Meeting}.}
\pubentry{2019}{Sever, G., Obabko, A., Jacob, R., \textbf{Jain, R.}, and Catlett, C. ``Simulations of Idealized and Real Urban Boundary Layer Environments Using NWP and CFD Models.'' \textit{18th Conference on Mesoscale Processes}.}
\pubentry{2019}{Jacob, R. L., Sever, G., Obabko, A., \textbf{Jain, R.}, and Catlett, C. E. ``CFD Simulations of Flow in Realistic Urban Geometries Initialized from Weather Models.'' \textit{AGU Fall Meeting}.}
\pubentry{2018}{Obabko, A., \textbf{Jain, R.}, Jacob, R., Paoli, R., Sever, G., Grindeanu, I., and Fischer, P. ``Nek5000 Wall-Resolved LES for Urban Geometries.'' \textit{10th International Conference on Urban Climate / 14th Symposium on the Urban Environment}.}
\pubentry{2018}{Silva, M. P., Sharma, A., Budhathoki, M., \textbf{Jain, R.}, and Catlett, C. E. ``Neighborhood Scale Heat Mitigation Strategies Using Array of Things Data in Chicago.'' \textit{AGU Fall Meeting}.}
\pubentry{2018}{Sever, G., Jacob, R., and \textbf{Jain, R.} ``Mesoscale to Microscale Weather Simulations over the Chicago Downtown Region.'' \textit{10th International Conference on Urban Climate / 14th Symposium on the Urban Environment}.}

\section{Technical Reports, Manuals, and Other Publications}
\pubentry{2020}{Goldring, N., Bruhwiler, D., Nash, B., Wu, Z., Nagler, R., Carter, J., Lerch, J., Suthar, K., Den Hartog, P., \textbf{Jain, R.}, and Mahadevan, V. ``Multiphysics Design and Optimization of Complex Vacuum Chambers (Phase II Final Technical Report).''}
\pubentry{2017}{\textbf{Jain, R.} ``Reactor Geometry (\&Mesh) Generator Users Manual.''}
\pubentry{2016}{\textbf{Jain, R.}, Vanderzee, E., Grindeanu, I., and Mahadevan, V. ``Mesh Generation and Algorithm Development for NEAMS.''}
\pubentry{2015}{\textbf{Jain, R.}, Vanderzee, E., and Mahadevan, V. ``Update on Development of Mesh Generation Algorithms in MeshKit.'' ANL/MCS-TM-355.}
\pubentry{2015}{\textbf{Jain, R.} and Mahadevan, V. ``Documentation for MeshKit-Reactor Geometry (\&mesh) Generator.'' ANL/MCS-TM-354.}
\pubentry{2015}{Mahadevan, V., Grindeanu, I. R., Ray, N., \textbf{Jain, R.}, and Wu, D. ``SIGMA Release v1.2: Capabilities, Enhancements and Fixes.'' ANL/MCS-TM-357.}
\pubentry{2015}{Merzari, E., Shemon, E. R., Yu, Y., Thomas, J. W., Obabko, A., \textbf{Jain, R.}, Mahadevan, V., Solberg, J., Ferencz, R., and Whitesides, R. ``Full Core Multiphysics Simulation with Offline Mesh Deformation.'' ANL/NE-15/42.}
\pubentry{2015}{Merzari, E., Shemon, E. R., Yu, Y. Q., Thomas, J. W., Obabko, A., \textbf{Jain, R.}, Mahadevan, V., Tautges, T., Solberg, J., Ferencz, R. M., and Whitesides, R. ``Multi-physics Demonstration Problem with the SHARP Reactor Simulation Toolkit.'' ANL/NE-15/44.}
\pubentry{2014}{\textbf{Jain, R.} ``Report on FY11 Extensions to MeshKit and RGG.'' ANL/MCS-TM-316.}
\pubentry{2014}{\textbf{Jain, R.} and Mahadevan, V. ``2014 MeshKit Release.'' ANL/MCS-TM-344.}
\pubentry{2014}{Tautges, T. J. and \textbf{Jain, R.} ``Mesh Copy/Move/Merge Tool for Reactor Simulation Applications.'' ANL/MCS-TM-343.}
\pubentry{2013}{Tautges, T. J., Fischer, P., Grindeanu, I., \textbf{Jain, R.}, Mahadevan, V., Obabko, A., Smith, M. A., Merzari, E., and Ferencz, R. M. ``SHARP Assembly-Scale Multiphysics Demonstration Simulations.'' ANL/NE-13/9.}
\pubentry{2013}{\textbf{Jain, R.} and Tautges, T. J. ``MeshKit.'' ANL/MCS-TM-336.}
\pubentry{2012}{Tautges, T. J., Fischer, P., Grindeanu, I., \textbf{Jain, R.}, Mahadevan, V., Obabko, A., Smith, M. A., Hamilton, S., Clarno, K., and Baird, M. ``A Coupled Thermal / Hydraulics -- Neutronics -- Fuel Performance Analysis of an SFR Fuel Assembly.'' Report to the U.S. Department of Energy.}

\section{Software and Open Source}
\begin{tabularx}{\textwidth}{@{}p{2.0cm}X@{}}
\textbf{UXarray} & Lead developer for open-source Python tooling for unstructured grid analysis. \href{https://github.com/UXARRAY/uxarray}{GitHub} and \href{https://uxarray.readthedocs.io}{documentation}. \\[4pt]
\textbf{FLASH-X} & I/O and compression lead for a million-line multiphysics simulation code used in astrophysics, combustion, and fluid dynamics. \\[4pt]
\textbf{CANDLE / IMPROVE} & Engineering support for HPO, benchmarking, and reproducible model workflows for cancer AI research. \\[4pt]
\textbf{Pangu-Weather} & PyTorch workflow for AI weather modeling adapted to Intel GPUs on Aurora. \\[4pt]
\textbf{MeshKit} & Principal investigator for reactor geometry and mesh generation tooling. \href{https://bitbucket.org/fathomteam/meshkit}{Source}. \\
\end{tabularx}

\section{Professional Service}
\begin{itemize}
  \item SBIR / STTR proposal reviewer for the U.S. Department of Energy.
  \item Panelist, ``Revolutionizing Public Infrastructure: The Impact of AI and Machine Learning,'' 5th Infraday Midwest Event.
  \item Reviewer for the \textit{Journal of Open Research Software} and NumGrid.
  \item Program committee member, NumGrid 2020.
  \item Session chair, Computational Geometries session, MC2015.
  \item Member, American Nuclear Society (2012 -- 2016).
  \item Volunteer, South Side Science Festival, University of Chicago (2023, 2024).
\end{itemize}

\section{Mentorship}
\begin{itemize}
  \item Mentored students, research aides, and staff on scientific Python, HPC workflows, systems engineering, and reproducible software development.
  \item Rylie Weaver (Research Aide, 2022 -- 2024): IMPROVE project, HPO techniques for cancer drug response prediction.
  \item Aaron Zedwick (Student, 2023 -- 2024): UXarray development, dual mesh routines, and remapping functionality.
  \item Mark Bartoszek (Systems Administration, 2023): mentoring on systems administration practices at Argonne.
\end{itemize}

\end{document}
