\documentclass[10pt,letterpaper]{article}
\usepackage[letterpaper,margin=0.75in]{geometry}
\usepackage{mdwlist}
\usepackage{enumitem}
\usepackage[utf8]{inputenc}
\usepackage{textcomp}
\usepackage{hyperref}
\usepackage{xcolor}

% Define custom colors
\definecolor{linkcolor}{HTML}{0066CC}
\definecolor{namecolor}{HTML}{003366}
\definecolor{sectioncolor}{HTML}{004C99}
\definecolor{subheadingcolor}{HTML}{444444}
\definecolor{datecolor}{HTML}{666666}
\definecolor{iconcolor}{HTML}{3399CC}

\hypersetup{
    colorlinks=true,
    linkcolor=linkcolor,
    filecolor=linkcolor,
    urlcolor=linkcolor,
    citecolor=linkcolor,
}

\urlstyle{same}
\usepackage{fontawesome5}
\usepackage{titlesec}
\titlespacing*{\section}{0pt}{1.5ex plus 1ex minus .2ex}{1.0ex plus .2ex}
\titlespacing*{\subsection}{0pt}{1.0ex plus 1ex minus .2ex}{0.5ex plus .2ex}
\titleformat{\section}{\Large\bfseries\color{sectioncolor}}{}{0em}{}
\titleformat{\subsection}{\large\bfseries\color{subheadingcolor}}{}{0em}{}
\pagestyle{empty}

% Updated resume macros with color for date and location
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*, itemsep=2pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}}
\newcommand{\resumeSubheading}[4]{\item \textbf{\color{subheadingcolor}#1} \hfill {\color{datecolor}#2} \\ \textit{\color{sectioncolor}#3} \hfill \textit{\color{datecolor}#4}}
\newcommand{\resumeProject}[2]{\item \textbf{\color{subheadingcolor}#1} \hfill {\color{datecolor}#2}}
\newcommand{\resumeItem}[1]{\item{#1}}

\begin{document}

\begin{center}
    {\Huge \textbf{\color{namecolor}Rajeev Jain}} \\ \vspace{2mm}
    Chicago, IL \\
    {\color{iconcolor}\faEnvelope} \href{mailto:rajeeja@gmail.com}{rajeeja@gmail.com} \quad
    {\color{iconcolor}\faPhone} (312) 725-3380 \quad
    {\color{iconcolor}\faLinkedin} \href{https://www.linkedin.com/in/rajeeja/}{linkedin.com/in/rajeeja} \\
    {\color{iconcolor}\faGoogle} \href{https://scholar.google.com/citations?user=bC77n9MAAAAJ&hl=en}{Google Scholar} \quad
    {\color{iconcolor}\faGithub} \href{https://github.com/rajeeja}{github.com/rajeeja} \quad
    {\color{iconcolor}\faGlobe} \href{https://rajeeja.github.io/}{rajeeja.github.io}
\end{center}

\section*{Experience}
\vspace{-0.5em}
\resumeSubHeadingListStart

\resumeSubheading{CASE Staff At-Large}{Sep 2023 -- Present}{The University of Chicago (UChicago)}{Chicago, IL}
\resumeItemListStart
  \resumeItem{Joint appointment supporting computational cancer research initiatives between Argonne National Laboratory (ANL) and UChicago.}
\resumeItemListEnd

\resumeSubheading{Principal Specialist, Research Software Engineering (formerly Research Software Developer)}{Aug 2009 -- Present}{Mathematics and Computer Science Division, Argonne National Laboratory (ANL)}{Lemont, IL}
\resumeItemListStart
  \resumeItem{Delivered reliable research software across cancer data science, climate computation, multiphysics simulation, urban systems, and reactor modeling.}
  \resumeItem{Partnered with domain scientists and engineers to turn prototypes into maintainable, tested tools used at DOE facilities.}
  \resumeItem{Mentored junior researchers; emphasized performance, reproducibility, and clear engineering practices.}
\resumeItemListEnd

\resumeSubheading{Research and Teaching Assistant}{Aug 2007 -- Jul 2009}{Structural Engineering, Arizona State University}{Tempe, AZ}
\resumeItemListStart
  \resumeItem{Researched FEM-based shape optimization for blast-resistant structural design sponsored by the U.S. Army Research Office; supported structural engineering courses and labs.}
\resumeItemListEnd

\resumeSubheading{Project Engineer}{May 2006 -- Jun 2007}{Wipro Technologies}{Bangalore/Hyderabad, India}
\resumeItemListStart
  \resumeItem{Developed production-ready code in Java and SAP; quickly adapted to large-scale software environments.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section*{Awards}
\begin{itemize}[leftmargin=*, itemsep=1pt]
  \item \textbf{R\&D 100 Award (2023):} CANDLE/Supervisor — \href{https://www.rdworldonline.com/candle-cancer-distributed-learning-environment-is-the-rd-100-winner-of-the-day/}{RDWorld}; coverage: \href{https://nvidianews.nvidia.com/news/nvidia-teams-with-national-cancer-institute-u-s-department-of-energy-to-create-ai-platform-for-accelerating-cancer-research}{NVIDIA News}, \href{https://cacm.acm.org/news/combating-cancer-with-data/}{CACM}
  \item \textbf{R\&D 100 Award (2022):} FLASH-X — \href{https://www.rdworldonline.com/rd-100-2022-winner/flash-x-a-multiphysics-simulation-software/}{RDWorld}
\end{itemize}

\section*{Major Projects}
\vspace{-0.5em}
\resumeSubHeadingListStart
\resumeProject{IMPROVE/CANDLE (Cancer Data Science - ECP)}{Jan 2017 -- Present}
\resumeItemListStart
  \resumeItem{Led CANDLE/Supervisor across DOE supercomputers; standardized experiments and HPO; \textbf{R\&D 100 (2023)}.}
  \resumeItem{Improved reproducibility and fair model comparisons; widely cited and covered by NVIDIA News and CACM.}
\resumeItemListEnd

\resumeProject{Uxarray (Climate Computation/Modeling - DOE)}{Jun 2021 -- Present}
\resumeItemListStart
  \resumeItem{Co-created a Python toolkit for unstructured climate grids; enabled up to 60x speed-ups via vectorization and parallelization; adopted by DOE climate users.}
\resumeItemListEnd

\resumeProject{FLASH-X (Multiphysics Simulation, Astrophysics - ECP)}{Jun 2016 -- Sep 2023}
\resumeItemListStart
  \resumeItem{Implemented asynchronous HDF5 I/O with compression; \textbf{R\&D 100 (2022)}; improved I/O-bound runs by more than 20\%.}
  \resumeItem{Architected a verification framework with nightly testing and baselines to stabilize releases.}
\resumeItemListEnd

\resumeProject{Urban Coupled Simulations (ECP Seed Funded)}{Jun 2016 -- Sep 2018}
\resumeItemListStart
  \resumeItem{Built coupling and data pipelines integrating high-fidelity weather with building energy models for city-scale analysis.}
\resumeItemListEnd

\resumeProject{SIGMA/MeshKit/RGG (Nuclear Reactor Simulations - DOE NEAMS)}{Aug 2009 -- Sep 2018}
\resumeItemListStart
  \resumeItem{Led MeshKit/DAG and RGG tools; advised Kitware during SBIR commercialization; reduced reactor core modeling time from weeks to hours.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section*{Open-Source Contributions}
\begin{itemize}[leftmargin=*, itemsep=1pt]
  \item \textbf{UXarray:} \href{https://github.com/UXARRAY/uxarray/}{github.com/UXARRAY/uxarray} — unstructured climate grids toolkit (Python)
  \item \textbf{FLASH-X:} Asynchronous I/O and verification contributions — \href{https://flash-x.org/}{flash-x.org}
  \item \textbf{CANDLE/Supervisor:} Workflow framework for ML — \href{https://github.com/ECP-CANDLE/Supervisor}{github.com/ECP-CANDLE/Supervisor}
\end{itemize}

\section*{Selected Publications}
\begin{itemize}[leftmargin=*, itemsep=1pt]
  \item Wozniak, J. M., \textbf{Jain, R.}, et al. (2018). CANDLE/Supervisor. \textit{BMC Bioinformatics}. \href{https://doi.org/10.1186/s12859-018-2056-3}{doi:10.1186/s12859-018-2056-3}
  \item Mahadevan, V. S., Merzari, E., Tautges, T., \textbf{Jain, R.}, et al. (2014). High-resolution coupled physics solvers. \textit{Phil. Trans. R. Soc. A}. \href{https://doi.org/10.1098/rsta.2013.0381}{doi:10.1098/rsta.2013.0381}
  \item \textbf{Jain, R.}, Luo, X., Sever, G., Hong, T., \& Catlett, C. (2020). Urban weather boundary conditions. \textit{Journal of Building Performance Simulation}. \href{https://doi.org/10.1080/19401493.2020.1739106}{doi:10.1080/19401493.2020.1739106}
  \item \textbf{Jain, R.}, \& Tautges, T. J. (2012). Geometry and mesh models for reactor cores using a lattice hierarchy. \textit{Engineering with Computers}. \href{https://doi.org/10.1007/s00366-011-0221-4}{doi:10.1007/s00366-011-0221-4}
  \item Dhruv, A., \textbf{Jain, R.}, et al. (2023). Verification of Flash-X. \textit{ICSE Companion}. \href{https://doi.org/10.1109/ICSE-Companion60176.2023.00107}{doi:10.1109/ICSE-Companion60176.2023.00107}
  \item \textbf{Jain, R.}, et al. (2025). UXarray: Extending Xarray for Unstructured Grids. \textit{EGU General Assembly}. \href{https://doi.org/10.5194/egusphere-egu25-13873}{doi:10.5194/egusphere-egu25-13873}
\end{itemize}

\section*{Teaching \& Mentoring}
\begin{itemize}[leftmargin=*, itemsep=1pt]
  \item TA/RA at Arizona State University (2007--2009): blast mitigation research (U.S. Army Research Office) and structural engineering instruction.
\end{itemize}

\section*{Talks \& Media}
\begin{itemize}[leftmargin=*, itemsep=1pt]
  \item SciPy: UXarray for Unstructured Grids — \href{https://www.youtube.com/watch?v=qwqJeOO8m6A&t=545s}{YouTube}
  \item HDF5 Annual Meeting: FLASH-X Async I/O — \href{https://www.youtube.com/watch?v=MuifQ7lHRR8&t=176s}{YouTube}
\end{itemize}

\section*{Technical Skills}
\resumeSubHeadingListStart
  \item \textbf{HPC and Programming:} Python, Fortran, C++; MPI, OpenMP, HDF5, parallel I/O, performance tuning on supercomputers.
  \item \textbf{ML and Data Tools:} PyTorch, Keras, NumPy, Matplotlib, pandas, Scikit-learn, Jupyter; software engineering with Git, CI/CD.
\resumeSubHeadingListEnd

\section*{Education}
\resumeSubHeadingListStart
\resumeSubheading{The University of Chicago}{Chicago, IL}{M.S. in Computer Science}{Jun 2020}
\resumeSubheading{Arizona State University}{Tempe, AZ}{M.S. in Structural Engineering (Minor: Computer Science)}{Jul 2009}
\resumeSubheading{Indian Institute of Technology (IIT) Dhanbad}{Dhanbad, India}{B.Tech. in Mechanical Engineering}{May 2006}
\resumeSubHeadingListEnd

\end{document}
