%-------------------------
% Resume in LaTeX - One Page Version
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\Huge \scshape Rajeev Jain} \\ \vspace{8pt}
    \small 
    \href{mailto:rajeeja@gmail.com}{\raisebox{-0.2\height}\faEnvelope\ rajeeja@gmail.com} ~ 
    \href{https://github.com/rajeeja}{\raisebox{-0.2\height}\faGithub\ rajeeja} ~
    \href{https://linkedin.com/in/rajeeja}{\raisebox{-0.2\height}\faLinkedin\ rajeeja} ~
    \href{https://rajeeja.github.io}{\raisebox{-0.2\height}\faGlobe\ rajeeja.github.io}
    \vspace{-8pt}
\end{center}

\section{Summary}
Research software engineer building high-performance tools for climate science, cancer research, and exascale computing. Lead developer of UXarray (205+ GitHub stars), 2× R\&D 100 Award winner, with 16+ years optimizing scientific workflows at Argonne National Laboratory.

\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Principal Specialist, Research Software Engineering}{2009 -- Present}
      {Argonne National Laboratory $\cdot$ Joint Appointment, University of Chicago}{Chicago, IL}
      \resumeItemListStart
        \resumeItem{\textbf{UXarray (2022--Present):} Lead developer for Python library enabling analysis of multi-petabyte unstructured climate datasets. Implemented conservative zonal averaging using Gauss-Legendre quadrature, Grid I/O readers for ESMF, MPAS, SCRIP, and HEALPix formats, and comprehensive testing infrastructure. Established CI/CD pipeline with GitHub Actions and regular PyPI releases. Presented tutorials at SC24, AMS 2024, and ESDS Annual Event. \textbf{205+ GitHub stars, adopted by NCAR, DOE labs, and universities worldwide.}}
        \resumeItem{\textbf{FLASH-X (2019--2024):} Implemented asynchronous HDF5 I/O achieving \textbf{40-70\% reduction} in checkpoint write times on Summit supercomputer. Integrated SZ3 and ZFP compression algorithms reducing storage requirements by \textbf{50\%+} with minimal accuracy loss. Built verification workflow with nightly baseline testing. Published at SC24 10th International Workshop on Data Analysis and Reduction. \textbf{R\&D 100 Award 2022.}}
        \resumeItem{\textbf{CANDLE/IMPROVE (2020--2025):} Built hyperparameter optimization infrastructure running \textbf{10,000+ training experiments} across Summit, Theta, and Cori supercomputers. Developed GitHub Actions workflows for cross-study validation and Docker-based reproducibility. Maintained benchmarking framework used by \textbf{15+ researchers}. Results published in Briefings in Bioinformatics (2025). \textbf{R\&D 100 Award 2023.}}
        \resumeItem{\textbf{Urban ECP \& MeshKit (2009--2019):} Led bi-weekly coordination across 4 national labs for urban microclimate simulation project. Coupled WRF weather models with Nek5000 CFD simulations achieving 11\% improvement in building energy prediction accuracy. Developed parallel reactor core mesh generator creating billion-element hex meshes. Published in Engineering with Computers. \textbf{Best Paper Award, IMR 2010.}}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {M.S. in Computer Science}{2020}
      {University of Chicago}{Chicago, IL}
    \resumeSubheading
      {M.S. in Structural Engineering}{2009}
      {Arizona State University $\cdot$ Graduate Fellowship Recipient}{Tempe, AZ}
    \resumeSubheading
      {B.Tech in Mechanical Engineering}{2006}
      {Indian Institute of Technology (IIT), Indian School of Mines}{Dhanbad, India}
  \resumeSubHeadingListEnd

\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages:} Python, C++, Fortran, R, Bash \\
     \textbf{ML/Data Science:} PyTorch, TensorFlow, NumPy, Pandas, Xarray, Scikit-learn, Parsl, Swift/T \\
     \textbf{HPC/Systems:} MPI, OpenMP, HDF5, NetCDF, Docker, Singularity, Git, GitHub Actions, Jenkins \\
     \textbf{Domains:} Climate modeling, cancer pharmacogenomics, computational physics, mesh generation
    }}
 \end{itemize}

\section{Selected Publications \& Presentations}
\resumeSubHeadingListStart
  \resumeItem{Partin, A., Vasanthakumari, P., Narykov, O., Wilke, A., Jain, R., et al. (2025). "Benchmarking community drug response prediction models: datasets, models, tools, and metrics." \textit{Briefings in Bioinformatics} (forthcoming).}
  \resumeItem{Jain, R., Tang, H., Dhruv, A., Byna, S. (2024). "Enabling Data Reduction for Flash-X Simulations." \textit{10th International Workshop on Data Analysis and Reduction for Big Scientific Data}, SC24.}
  \resumeItem{Jain, R., Wozniak, J., Partin, A., et al. (2024). "Cross-HPO: Optimizing Neural Networks for Cancer Drug Response Using Hyperparameter Tuning on Multiple Datasets." \textit{Tenth Computational Approaches for Cancer Workshop}, SC24.}
  \resumeItem{Chmielowiec, P., Chen, H., Jacob, R., Jain, R., et al. (2024). "UXarray: Extending Xarray with Support for Unstructured Grids." \textit{104th AMS Annual Meeting}.}
  \resumeItem{Tautges, T. J., Jain, R. (2011). "Creating Geometry and Mesh Models for Nuclear Reactor Core Geometries Using a Lattice Hierarchy-Based Approach." \textit{Engineering with Computers}.}
\resumeSubHeadingListEnd

\end{document}
