\documentclass[10pt,letterpaper]{article}
\usepackage[letterpaper,margin=0.75in]{geometry}
\usepackage{mdwlist}
\usepackage[utf8]{inputenc}
\usepackage{textcomp}
\usepackage{hyperref}
\usepackage{xcolor}

% Define custom colors
\definecolor{linkcolor}{HTML}{0066CC}
\definecolor{namecolor}{HTML}{003366}
\definecolor{sectioncolor}{HTML}{004C99}
\definecolor{subheadingcolor}{HTML}{444444}
\definecolor{datecolor}{HTML}{666666}

\hypersetup{
    colorlinks=true,
    linkcolor=linkcolor,
    filecolor=linkcolor,
    urlcolor=linkcolor,
    citecolor=linkcolor,
}

\urlstyle{same}
\pagestyle{empty}

% Resume macros
\newcommand{\resumeSubHeadingListStart}{\begin{list}{}{\setlength{\leftmargin}{0pt}\setlength{\itemsep}{0pt}}}% no bullets
\newcommand{\resumeSubHeadingListEnd}{\end{list}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}}
\newcommand{\resumeSubheading}[4]{\item \textbf{\color{subheadingcolor}#1} \hfill {\color{datecolor}#2} \\ \textit{\color{sectioncolor}#3} \hfill \textit{\color{datecolor}#4}}
\newcommand{\resumeProject}[2]{\item \textbf{\color{subheadingcolor}#1} \hfill {\color{datecolor}#2}}
\newcommand{\resumeItem}[1]{\item{#1}}

\begin{document}

\begin{center}
    {\Huge \textbf{\color{namecolor}Rajeev Jain}} \\ \vspace{2mm}
    Chicago, IL \\
    Email: \href{mailto:rajeeja@gmail.com}{rajeeja@gmail.com} \quad
    Phone: (312) 725-3380 \quad
    LinkedIn: \href{https://www.linkedin.com/in/rajeeja/}{linkedin.com/in/rajeeja} \\
    Scholar: \href{https://scholar.google.com/citations?user=bC77n9MAAAAJ&hl=en}{scholar.google.com} \quad
    GitHub: \href{https://github.com/rajeeja}{github.com/rajeeja} \quad
    Web: \href{https://rajeeja.github.io/}{rajeeja.github.io}
\end{center}

\section*{Summary}
\begin{itemize}
  \item Research software engineer with 16+ years building scientific software across climate, cancer data science, multiphysics simulation, urban systems, and nuclear engineering.
  \item Focus areas: parallel input/output, profiling and optimization, reproducibility, scalable pipelines, and Python programming.
  \item Scope includes multi-institution projects, exascale-class systems, and software practices around testing, continuous integration, and releases.
\end{itemize}

\section*{Experience}
\vspace{-0.5em}
\resumeSubHeadingListStart
\resumeSubheading{Research Software Engineering Roles (current: Principal Specialist)}{Aug 2009 -- Present}{Mathematics and Computer Science Division, Argonne National Laboratory}{Lemont, IL}
\resumeItemListStart
\resumeItem{Built and maintained research software across UXarray, FLASH-X, Cancer Distributed Learning Environment (CANDLE) workflows, MeshKit, Reactor Geometry Generator, and urban simulation workflows.}
  \resumeItem{Implemented conservative zonal averaging in UXarray (pull request \#1345) and contributed to regular Python Package Index releases.}
  \resumeItem{Ran large-scale hyperparameter optimization workflows for cancer data science projects; standardized reproducibility and benchmarking pipelines.}
  \resumeItem{Implemented asynchronous Hierarchical Data Format 5 (HDF5) input/output and compression for FLASH-X; reduced input/output time in benchmarks (20\%+).}
  \resumeItem{Work spans exascale-class systems and large-scale workflows.}
\resumeItemListEnd

\resumeSubheading{Staff At-Large}{Sep 2023 -- Present}{The University of Chicago}{Chicago, IL}
\resumeItemListStart
  \resumeItem{Joint appointment supporting cancer and earth science research.}
\resumeItemListEnd

\resumeSubheading{Research and Teaching Assistant}{Aug 2007 -- Jul 2009}{Arizona State University}{Tempe, AZ}
\resumeItemListStart
  \resumeItem{Researched finite element method-based shape optimization for blast-resistant design and supported structural engineering courses.}
\resumeItemListEnd

\resumeSubheading{Project Engineer}{May 2006 -- Jun 2007}{Wipro Technologies}{Bangalore/Hyderabad, India}
\resumeItemListStart
  \resumeItem{Developed production software in Java and enterprise resource planning systems in large enterprise environments.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section*{Selected Projects}
\vspace{-0.5em}
\resumeSubHeadingListStart
\resumeProject{UXarray (Climate Computing)}{2021 -- Present}
\resumeItemListStart
  \resumeItem{Core contributor to a Python toolkit for unstructured climate grids; focused on scalable analysis and conservative averaging.}
\resumeItemListEnd

\resumeProject{FLASH-X (Multiphysics Simulation)}{2016 -- 2023}
\resumeItemListStart
  \resumeItem{Built async input/output and verification workflows; contributed to Research and Development 100 Award (2022).}
\resumeItemListEnd

\resumeProject{Cancer Data Science (CANDLE workflows)}{2017 -- Present}
\resumeItemListStart
  \resumeItem{Standardized pipelines and hyperparameter optimization workflows for reproducible model evaluation.}
\resumeItemListEnd

\resumeProject{MeshKit and Reactor Geometry Generator (Reactor Modeling)}{2009 -- 2018}
\resumeItemListStart
  \resumeItem{Principal investigator for Nuclear Energy Advanced Modeling and Simulation meshing; reduced reactor core modeling time from weeks to hours; Small Business Innovation Research commercialization with Kitware.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section*{Education}
\vspace{-0.5em}
\resumeSubHeadingListStart
\resumeSubheading{The University of Chicago}{Chicago, IL}{Master of Science in Computer Science}{Jun 2020}
\resumeSubheading{Arizona State University}{Tempe, AZ}{Master of Science in Structural Engineering (Minor: Computer Science)}{Jul 2009}
\resumeSubheading{Indian Institute of Technology Dhanbad}{Dhanbad, India}{Bachelor of Technology in Mechanical Engineering}{May 2006}
\resumeSubHeadingListEnd

\section*{Awards}
\begin{itemize}
  \item Research and Development 100 (R\&D 100) Awards: \href{https://www.rdworldonline.com/candle-cancer-distributed-learning-environment-is-the-rd-100-winner-of-the-day/}{CANDLE / Supervisor (2023)} and \href{https://www.rdworldonline.com/rd-100-2022-winner/flash-x-a-multiphysics-simulation-software/}{FLASH-X (2022)}.
  \item Best Paper, International Meshing Roundtable (2010).
  \item University Graduate Fellowship, Arizona State University (2007--2009).
  \item Small Business Innovation Research (SBIR) Phase I and II awards for Reactor Geometry Generator commercialization with Kitware (2014--2017).
\end{itemize}

\section*{Selected Publications}
\begin{itemize}
  \item UXarray: \href{https://eesm.science.energy.gov/presentations/uxarray-python-package-analysis-and-visualization-model-output-unstructured-climate}{UXarray presentation and paper}.
  \item FLASH-X: \href{https://arxiv.org/abs/2208.11630}{Paper 1} and \href{https://ieeexplore.ieee.org/document/10026923}{Paper 2}.
  \item CANDLE: \href{https://pubmed.ncbi.nlm.nih.gov/30577736/}{Supervisor workflow} and \href{https://web.cels.anl.gov/~woz/papers/Counterfactuals_2021.pdf}{Counterfactual analysis}.
  \item Urban microclimate: \href{https://eta-publications.lbl.gov/sites/default/files/17_-_urban_weather_boundary_conditions_-_tianzhen_hong.pdf}{Boundary conditions paper}.
\end{itemize}

\section*{Technical Skills}
\resumeSubHeadingListStart
  \item \textbf{High-performance computing and programming:} Python, C++, Fortran; Message Passing Interface (MPI), Open Multi-Processing (OpenMP), HDF5, parallel input/output, performance tuning.
  \item \textbf{Machine learning and data tools:} PyTorch, Keras, NumPy, pandas; Git, continuous integration/continuous delivery.
\resumeSubHeadingListEnd

\end{document}
